\documentclass[../main/main.tex]{subfiles}

\begin{document}

\section{Meeting on 6 September 2019}
\begin{itemize}
\item overview of Petnica summer institute on Astrophysics

\item question: manual by Puls: why is isotropic distribution sampled from $\mu \mu$?

\item \texttt{pcyg.f90} program

\item practical arangements  

\item SKIRT code 
\item discussion of paper (Dimarco+2018)
\end{itemize}

\section{Meeting on 23 September 2019}
\begin{itemize}
\item convergence plots
\item relation $N \sim \tau + \tau^2/2$
\item limb darkening
\end{itemize}

\section{Meeting on 30 September 2019}
\begin{itemize}
\item discussion about $x_{\text{min}}$ and $x_{\text{max}}$
\item discussion about introduction of second line. 
\begin{itemize}
\item take into account the Doppler shift because you have two different frames

\item make them radially streaming (release)
\item do step for step:
\begin{itemize}
\item begin with creating a correct well
\end{itemize}
\end{itemize}

\item normalized frequency: $x = \frac{\nu - \nu_0}{\nu_ 0}\frac{c}{v_{infty}}$

\item adding other resonance frequencies, involves enlarging the frequency frame.

\item about the goal of the master thesis. Making a master thesis is not doing a course where all is well-defined and \textit{a priori} known.
\end{itemize}

\section{Meeting on 30 October}
with Dylan and Luka.
\begin{itemize}
\item question about MC limb darkening

\item the quantity $\dot{M}$ is a constant. From continuity of mass
\begin{equation}
\frac{d\rho}{dt}  + \nabla.(\rho v) = 0
\end{equation}
In steady-state and in sperical symmetry
\begin{equation}
\frac{1}{r^2}\frac{\partial (r^2 \rho v)}{\partial r} = 0
\end{equation}

\item discussion about computing luminosity for pcyg profile. Take into account changing frequency for energy balance.

\item change $\frac{dL}{dr}$ into $\frac{dL_{\nu}}{dr}$
\end{itemize}


\end{document}